Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-06-01 paper.tex
Update data access section

\subsection{Data preprocessing}
\label{sec:data_preprocessing}
The findings of this study are
based on sequences and metadata available on GISAID (\url{https://gisaid.org/})
up to 2022-08-22 and accessible at
% Do we need to upload a separate Table or is this DOI sufficient?
\url{https://doi.org/10.55876/gis8.230329cd}.
We removed sequences
if they had ambiguous collection dates, were collected before 2020-01-01
or were isolated from a non-human host.
We aligned sequences to the Wuhan-Hu-1/2019 reference sequence
(GenBank: MN908947.3) using Nextclade v2.3.0~\citep{Aksamentov2021-hj} (dataset tag
2022-07-26T12:00:00Z). We also excluded sequences if they had a
``bad'' quality control status
in any of the four Nextclade columns (``qc.missingData.status'',
``qc.mixedSites.status'', ``qc.frameShifts.status'' and `qc.stopCodons.status'').

@@

\section{Data Availability}
The source code for \texttt{sc2ts} is
available on GitHub
\url{https://github.com/jeromekelleher/sc2ts/}.
The Jupyter notebooks and code used to produce the results described here are also
available on GitHub \url{https://github.com/jeromekelleher/sc2ts-paper/}.

% TODO what's the right way to say this?
The inferred ARGs described here are available on request to those with
the appropriate GISAID data access.

>>>>

\subsection{Data preprocessing}
\label{sec:data_preprocessing}
The findings of this study are
based on sequences and metadata available on GISAID (\url{https://gisaid.org/})
up to 2022-08-22 and accessible at
\url{https://doi.org/10.55876/gis8.230329cd}.
We removed sequences
if they had ambiguous collection dates, were collected before 2020-01-01
or were isolated from a non-human host.
We aligned sequences to the Wuhan-Hu-1/2019 reference sequence
(GenBank: MN908947.3) using Nextclade v2.3.0~\citep{Aksamentov2021-hj} (dataset tag
2022-07-26T12:00:00Z). We also excluded sequences if they had a
``bad'' quality control status
in any of the four Nextclade columns (``qc.missingData.status'',
``qc.mixedSites.status'', ``qc.frameShifts.status'' and `qc.stopCodons.status'').

@@

\section{Data Availability}
The source code for \texttt{sc2ts} and notebooks and code used to produce the
results described here available on GitHub
at \url{https://github.com/jeromekelleher/sc2ts/}
and \url{https://github.com/jeromekelleher/sc2ts-paper/}.

Details of the GISAID data used are available at
\url{https://doi.org/10.55876/gis8.230329cd} and included in the
Supplemental Table.

The inferred ARGs described here are available on request to those with
the appropriate GISAID data access.
